The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-06-08 donde.tex
targeting paternalism rules

%Replace this paragraph with discussion of optimal targeting of paternalism
Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates. By over-collateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.  Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) may not be adequate. We hesitate to give precise policy recommendations since we don't have good measures of welfare. Even though the monthly payment contract dramatically reduces financial cost, it could potentially generate lower (or higher) anxiety. Moreover, frequent payment requirements may decrease welfare of highly impatient borrowers.\footnote{The paper presents an back of the envelope exercise that suggests annual discount rates of 4000 are necessary to nullify the reductions in financial cost we estimate. \hl{Note also that since the fee for skipping payment is 2\%, the iliquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.

@@

The results from Section \ref{experiment} show that commitment \emph{works}: clients who were assigned to the forced commitment arm experienced substantially lower financial costs on average.
In spite of this, given the opportunity, only \hl{11\%} of borrowers chose commitment. 
If the effect of commitment were homogeneous, this would be enough to conclude that the \hl{89\%} who did not choose it would have been financially better-off if they had.
In a world of heterogeneous treatment effects, however, low demand for commitment could still be consistent with individual rationality.
The borrowers who did not choose commitment could simply be those who don't need it. 
Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: Appendix \ref{append:chernozhukov} tests and rejects the null hypothesis of homogeneous treatment effects, following the methodology of \cite{chernozhukov2018generic}.
So the question remains: do the \hl{89\%} who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly mistake? 
In this section we now present a range of econometric exercises that shed light on this question, leveraging unique features of our experimental design. 
Despite substantial treatment effect heterogeneity, most borrowers would experience lower financial costs under a commitment contract. 
Indeed, commitment lowers average financial costs even for the subset of borrowers who would \emph{not} choose to commit voluntarily.
To simplify the exposition in this and all sections that follow, we re-define all outcome variables so that \emph{beneficial} treatment effects are \emph{positive}. Using this convention, a positive treatment effect of commitment on financial cost, for example, reflects the average cost \emph{savings} caused by commitment.

\subsubsection{Bounding the Distribution of Individual Treatment Effects}

If we knew the distribution $F_\Delta$ of individual treatment effects $\Delta_i \equiv Y_{i1} - Y_{i0}$, it would be easy assess how many individuals would win and lose under paternalism, along with the magnitude of any individual harm. 
%simply calculate $\mathbbm{P}(\Delta_i < 0)$.
Because we can never observe both $Y_{i0}$ and $Y_{i1}$ for the same borrower, $F_\Delta$ cannot be identified. 
It can, however, be bounded. 
%Using these bounds, we now show that more than \hl{11\%} of individual borrowers benefit from commitment.
Because it randomly assigns borrowers to the control and forced arms, our experimental design point identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$, call them $F_0$ and $F_1$.
Now, define the functions $\underline{F}$ and $\overline{F}$ as follows:
\[
\underline{F}(\delta) \equiv \max \left\{0, \sup_y F_1(y) - F_0(y - \delta)  \right\}, \quad
\overline{F}(\delta) \equiv 1 + \min \left\{0, \inf_y F_1(y) - F_0(y-\delta) \right\}.
\]
Since $F_0$ and $F_1$ are point identified, so are $\underline{F}$ and $\overline{F}$.
\cite{fan2010sharp} show that the sharp (best possible) pointwise bounds for $F_\Delta$ are given by $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$
These bounds are simple to compute, and can be surprisingly informative. 
Here we use them to bound the fraction of borrowers who benefit from commitment. 
Given the way that we have defined our outcome variables, this is the share of borrowers whose treatment effect is \emph{positive}, i.e.\ $1 - F_\Delta(0)$. 
To construct the sharp bounds for this quantity, we simply substitute $\delta = 0$ into the preceding equations and estimate $F_0$ and $F_1$ using their empirical analogues constructed from the forced commitment and forced no-commitment arms of the experiment.

Figure \ref{fig:FanPark} plots the sharp bounds for $F_{\delta}$ based on the APR outcome defined above in Section \ref{costs}. Our point estimates of $\underline{F}(0)$ and $\overline{F}_0$ are \hl{XXXX} and \hl{XXXX} respectively, with associated 95\% confidence intervals of \hl{XXXX} and \hl{XXXX}.\footnote{Confidence intervals are constructed using \hl{XXXX} bootstrap. See \cite{fan2010sharp} for details.}
%\todo[inline]{Issac: add in the confidence interval at $\delta = 0$ along with the figure \ref{fan_park_bounds}. These need to be the results that do not use covariates and we need to be careful about the sign convention for our effects. Frank follow-up to add 1-2 sentences discussing the results. Presumably we find that $F_\Delta(0) > 0.11$ this means that at least some people who choose not to commit \emph{must} be making a mistake, although we don't know who they are and this doesn't tell us how large the mistake is.}
An alternative way of presenting the \cite{fan2010sharp} bounds is in terms of quantiles of the distribution of $\Delta$. Let $0 < q < 1$, and define $Q_0, Q_1, Q$ to be the quantile functions corresponding to $F_0, F_1$ and $F_\Delta$.\footnote{In other words, $Q_0(q) \equiv \inf \{x | F(x) \geq q\}$ and so on.} Then the sharp bound for $Q_\Delta(q)$ is given by $\underline{Q}(q) \leq Q(q) \leq \overline{Q}(q)$ where
\[
\overline{Q}(q) \equiv \inf_{u \in [q,1]} [Q_1(u) - Q_0(u - q)], \quad
\underline{Q}(q) \equiv \sup_{u\in [0,q]} [Q_1(u) - Q_0(1 + u - q)]
\]
By substituting $q = 0.11$, these expressions allow us to bound the 11th percentile of the distribution of $\Delta$. Under a stylized Roy model in which borrowers with the largest (negative) treatment effects choose commitment, $Q(0.11)$ equals the treatment effect for the borrower at the margin of indifference between choosing commitment. 
Our point estimates for the lower and upper bounds $\underline{Q}(0.11)$ and $\overline{Q}(0.11)$ are \hl{XXXX} and \hl{XXXX} with corresponding 95\% confidence intervals \hl{XXXX} and \hl{XXXX}.\footnote{Again, confidence intervals are constructed using \hl{XXXX} bootstrap as describe in \cite{fan2010sharp}.}
%\todo[inline]{Issac: add the interval for $Q(0.11)$. Again, this needs to be without covariates and we need to be careful about the sign convention for our effects. Maybe we don't need a second figure with the confidence bands for the whole quantile function. Frank: add a sentence or two discussing the results. Presumably the aforementioned quantile is indeed negative and fairly large.}
Both ways of presenting the bounds yield the same conclusion: at least some borrowers who would benefit from commitment \emph{do not choose it} when offered.

@@

To understand the relationship between choice and heterogeneous treatment effects, it is important to be precise about the potential outcomes in our empirical setting.
Let $Z_i \in \{0, 1, 2\}$ denote the treatment arm to which to participant $i$ was assigned: $Z_i = 0$ denotes the forced no-commitment arm, $Z_i = 1$ denotes the forced commitment arm, and $Z_i = 2$ denotes the choice arm. 
Now let $D_i$ be the treatment that participant $i$ actually \emph{received}, where $D_i = 0$ denotes no-commitment and $D_i = 1$ denotes commitment. 
We assume perfect compliance in the $Z_i = 0$ and $Z_i = 1$ arms.\footnote{For more discussion on this point, see Section \ref{sec:integrity} above.}
It is only in the $Z_i = 2$ arm that participants are free to choose between alternative contracts. 
Let $C_i \in \{0, 1 \}$ denote a participant's ``choice type.'' If $C_i = 1$ then participant $i$ \emph{would choose commitment}, given the option; if $C_i = 0$ she would not. 
As shorthand, we call borrowers with $C_i = 1$ ``choosers'' and those with $C_i = 0$ ``non-choosers.''
Whereas a participant's choice type $C_i$ is only observed if she is allocated to the choice arm ($Z_i = 2$), her treatment $D_i$ and experimental arm $Z_i$ are always observed. 
Given the design of our experiment, these quantities are related by
\begin{equation}
D_i = \mathbbm{1}(Z_i \neq 2) Z_i + \mathbbm{1}(Z_i = 2) C_i.
\label{eq:potentialTreatments}
\end{equation}

We maintain the stable unit treatment value assumption (SUTVA) throughout. 
This means that borrower $i$'s outcomes depend only on her \emph{own} values of $Z_i$ and $D_i$, not those of any other person in the experiment: there are no \emph{spillovers}. 
Under this assumption, a fully general model for the potential outcomes in our experiment would take the form $Y_i(d, z)$ for $d\in \{0,1\}$ and $z \in \{0, 1, 2\}$, allowing participant $i$'s potential outcome to depend \emph{both} on the treatment she actually receives, $D_i$, and the experimental arm to which she is assigned, $Z_i$. 
This model is too general, however, to identify meaningful causal effects. 
For this reason, we impose two exclusion restrictions.
Before stating them, we first define some additional notation.
In particular, because any anyone with $Z_i = 0$ has $D_i = 0$ under our experimental design, we abbreviate the potential outcome $Y_i(d=0,z=0)$ as $Y_{i0}$. 
Similarly, as anyone with $Z_i = 1$ has $D_i = 1$, we abbreviate $Y_i(d=1,z=1)$ as $Y_{i1}$. 
Our first exclusion restriction is relevant only for non-choosers, individuals with $C_i = 0$, because they are the only borrowers for whom $D_i = 0$ when $Z_i = 2$.
We assume that
\begin{equation}
Y_i(d=0,z=2) = Y_i(d=0,z=0) \equiv Y_{i0}.
\label{eq:exclusion0}
\end{equation}
Equation \ref{eq:exclusion0} implies that every non-chooser experiences the same potential outcome when assigned to the control arm as when assigned to the choice arm.  
Our second exclusion is relevant only for choosers, individuals $C_i =1$, because they are the only borrowers for whom $D_i = 1$ when $Z_i = 2$.
We assume that 
\begin{equation}
Y_i(d=1,z=2) = Y_i(d=1,z=1)\equiv Y_{i1}.
\label{eq:exclusion1}
\end{equation}
Equation \ref{eq:exclusion1} implies that every chooser experiences the same potential outcome when assigned to the treatment arm as when assigned to the choice arm. 
Mathematically \eqref{eq:exclusion0} and \eqref{eq:exclusion0} have the same structure as the standard TOT or LATE exclusion restriction that $Y_i(d,z)$ depends only on $d$, not on $z$. 
Substantively, however, they are slightly different as there is no analogue of the ``chosen'' versus ``forced'' treatment distinction in the usual LATE setting.\footnote{See \cite{chamberlain2011bayesian}, who uses an assumption very similar to our exclusion restrictions to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.} 
Both \eqref{eq:exclusion0} and \eqref{eq:exclusion1} are plausible in our empirical setting. 
Moreover, each has testable implications that we fail to reject: see Appendix \ref{append:exclusion} for details. Under \eqref{eq:exclusion0} and \eqref{eq:exclusion1}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to  
\begin{equation}
    Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right].
\label{eq:potentialOutcomes}
\end{equation}
%\todo[inline]{Fix labels!}
%Accordingly, we impose the following standard exclusion restriction:
%\begin{equation}
%Y_i(d=0, z=0) = Y_i(d=0, z=2) \equiv Y_{i0}, \quad
%Y_i(d=1, z=1) = Y_i(d=1, z=2) \equiv Y_{i1}.
%\label{eq:exclusion}
%\end{equation}
%Equation \ref{eq:exclusion} says that each participant's potential outcome is the same regardless of whether she \emph{chooses} a particular treatment $D=d$ or is \emph{assigned} the same treatment. Viewing $Z_i$ as an instrumental variable (IV) for the treatment $D_i$, \eqref{eq:exclusion} amounts to the usual IV exclusion restriction.
%
%\todo[inline]{END Fix labels!}
Equation \ref{eq:potentialOutcomes} is the key to understanding the results that follows. 
By randomly assigning $Z_i=0$ and $Z_i = 1$, our experiment identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$ in the population as a whole. 
By randomly assigning $Z_i=2$, it likewise identifies the share of choosers ($C_i = 1$), the distribution of $Y_{i1}$ for choosers, and the distribution of $Y_{i0}$ for non-choosers ($C_i = 0$).
Because $Z_i$ is assigned independently of pre-treatment covariates $X_i$, our design also identifies the corresponding \emph{conditional} distributions of $Y_{i0}$ and $Y_{i1}$ given $X_i$. 
%These distributions are the ingredients that we use below to explore the importance of paternalism.

@@

Above we used outcome data from the forced arms ($Z_i\neq 2$) along with the commitment take-up rate in the choice arm ($Z_i = 2$) to argue that at least some of the \hl{89\%} of participants who did \emph{not} choose commitment would have been better off if they had. 
By additionally examining \emph{outcome data} in the choice arm, it is possible to say more. 
We now show how our experimental design, henceforth the ``controlled choice design,'' point identifies a number of interesting and economically-relevant causal quantities without the need for additional structural restrictions.
First we identify the treatment on the treated (ToT) and treatment on the untreated (TuT) effects, defined as follows:
\[
\text{ToT} \equiv \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 1), \quad
\text{TuT} \equiv \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0).
\]
%The TuT and ToT effects are particularly interesting for understanding the importance of paternalism. 
If the TuT is positive, this means that those who did not choose commitment would have experienced better outcomes, \emph{on average}, if they had. 
In a canonical Roy model, the ToT should exceed both the TuT and average treatment effect (ATE).
If the ToT is statistically distinguishable from and substantially larger than the TuT, this provides empirical support for the relevance of selection-on-gains in real-world decision-making.
Because our design identifies all three quantities, it allows us to test this implication directly and to calculate the average selection on gains (ASG):
\[
\text{ASG} \equiv \mathbbm{E}[Y_{i1} - Y_{i0}|C_i = 1] - \mathbb{E}[Y_{i1} - Y_{i0} | C_i = 0] = \text{ToT} - \text{TuT}.
\]
The controlled choice design also identifies both the average selection bias (ASB) and the average selection on levels (ASL). 
\[
\text{ASB} \equiv \mathbbm{E}[Y_{i0}|C_i = 1] - \mathbbm{E}[Y_{i0}|C_i = 0], \quad 
\text{ASL} \equiv \mathbbm{E}[Y_{i1}|C_i = 1] - \mathbbm{E}[Y_{i1}|C_i = 0].
\]
A companion STATA package accompanying this paper provides estimators of the ToT, TUT, ASG, ASB, and ASL, along with cluster-robust standard errors for each.\footnote{See Appendix \ref{append:randchoice} for more details.}

@@

\todo[inline]{Possibly add some discussion here of Craig's idea: using the controlled choice design to study ``targeting''}

@@

Table \ref{tot_tut} calculates the causal quantities described above--ToT, TuT, ASG, ASB, and ASL--for our experimental data, along with robust standard errors for each. 
For purposes of comparison, the table also presents the ATE results from Section \hl{XXXX} above (row 1), along with the corresponding average potential outcomes $\mathbbm{E}[Y_0]$ and $\mathbbm{E}[Y_1]$ (rows 4--5).
The columns of the table correspond to different outcome variables, defined as in Section \hl{XXXX} above.
For all four outcome definitions, the TuT effect is positive, statistically and economically significant, and comparable in magnitude to the ATE.
In other words: commitment is \emph{beneficial}, on average, to the people who \emph{would not choose it}, and these benefits are large.
The estimated ToT effects are positive and larger still.
Although we cannot quite reject the null hypothesis that the TuT and ToT effects are equal--our power is limited because of the low take-up rate of commitment in the choice arm--the pattern of coefficients is consistent with some degree of selection-on-gains.
Commitment is more beneficial to people who are willing to choose it than it is to people who are not.
For the APR benefit and (1 - Default) outcomes, we have sufficient precision to conclude that the average selection bias (ASB) is large and \emph{negative}.
This means that borrowers who choose commitment would have faced a \emph{higher} APR and probability of default under the status quo contract than borrowers who do not choose commitment. 
Overall, Table \ref{tot_tut} suggests that commitment works and the ``right people'' choose to commit: those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo. At the same time, \emph{not enough} people choose to commit: the commitment contract is beneficial on average even to those who would \emph{not} choose it voluntarily. Below we explore possible explanations for this result.

@@

@@

%\textit{Do file: } \texttt{fan\_park\_bnds,do}       
\end{figure}

>>>>

%Replace this paragraph with discussion of optimal targeting of paternalism
Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates. By over-collateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.  Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) may not be adequate. We hesitate to give precise policy recommendations since we don't have good measures of welfare. Even though the monthly payment contract dramatically reduces financial cost, it could potentially generate lower (or higher) anxiety. Moreover, frequent payment requirements may decrease welfare of highly impatient borrowers.\footnote{The paper presents an back of the envelope exercise that suggests annual discount rates of 4000 are necessary to nullify the reductions in financial cost we estimate. \hl{Note also that since the fee for skipping payment is 2\%, the illiquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.

@@

The results from Section \ref{experiment} show that commitment \emph{works}: clients who were assigned to the forced commitment arm experienced substantially lower financial costs on average.
In spite of this, given the opportunity, only \hl{11\%} of borrowers chose commitment. 
If the effect of commitment were homogeneous, this would be enough to conclude that the \hl{89\%} who did not choose it would have been financially better-off if they had.
In a world of heterogeneous treatment effects, however, low demand for commitment could still be consistent with individual rationality.
The borrowers who did not choose commitment could simply be those who don't need it. 
Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: Appendix \ref{append:chernozhukov} tests and rejects the null hypothesis of homogeneous treatment effects, following the methodology of \cite{chernozhukov2018generic}.
So the question remains: do the \hl{89\%} who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly mistake? 
In this section we present a number of econometric exercises that shed light on this question, leveraging unique features of our experimental design. 
Despite substantial treatment effect heterogeneity, most borrowers would experience lower financial costs under a commitment contract. 
Indeed, commitment lowers average financial costs even for the subset of borrowers who would \emph{not} choose to commit voluntarily.
To simplify the exposition in this and all sections that follow, we re-define all outcome variables so that \emph{beneficial} treatment effects are \emph{positive}. Using this convention, a positive treatment effect of commitment on financial cost, for example, reflects the average cost \emph{savings} caused by commitment.

\subsection{Bounding the Distribution of Individual Treatment Effects}
\label{sec:bounds}

If we knew the distribution of individual treatment effects, it would be easy assess how many individuals would win and lose under a policy of universal forced commitment, along with the magnitude of any individual harm. 
Because we can never simultaneously observe the same borrower in both the control and commitment arms, however, the distribution of individual treatment effects cannot be point identified.
It can, however, be bounded.
We begin our exploration of heterogeneous treatment effects by computing assumption-free bounds on the share of individuals who benefit from forced commitment.

Let $Y_{i0}$ be borrower $i$'s potential outcome under the control condition, $Y_{i1}$ be her potential outcome under forced commitment, and $\Delta_i \equiv Y_{i0} - Y_{i1}$.
Because it randomly assigns borrowers to the control and forced arms, our experimental design point identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$, call them $F_0$ and $F_1$.
Now, define the functions $\underline{F}$ and $\overline{F}$ as follows:
\[
\underline{F}(\delta) \equiv \max \left\{0, \sup_y F_1(y) - F_0(y - \delta)  \right\}, \quad
\overline{F}(\delta) \equiv 1 + \min \left\{0, \inf_y F_1(y) - F_0(y-\delta) \right\}.
\]
Since $F_0$ and $F_1$ are point identified, so are $\underline{F}$ and $\overline{F}$.
\cite{fan2010sharp} show that the sharp (best possible) pointwise bounds for $F_\Delta$ are given by $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$
These bounds are simple to compute, and can be surprisingly informative. 
Here we use them to bound the fraction of borrowers who benefit from forced commitment. 
Given the way that we have defined our outcome variables, this is the share of borrowers whose treatment effect is positive, i.e.\ $\mathbb{P}(\Delta_i > 0) = 1 - F_\Delta(0)$. 
To construct the sharp bounds for this quantity, we simply substitute $\delta = 0$ into the preceding equations and estimate $F_0$ and $F_1$ using their empirical analogues constructed from the forced commitment and forced no-commitment arms of the experiment.

Figure \ref{fig:FanPark} plots the sharp bounds for $F_{\delta}$ based on the APR outcome defined above in Section \ref{costs}. Our point estimates of $\underline{F}(0)$ and $\overline{F}_0$ are \hl{XXXX} and \hl{XXXX} respectively, with associated 95\% confidence intervals of \hl{XXXX} and \hl{XXXX}.\footnote{Confidence intervals are constructed using \hl{XXXX} bootstrap. See \cite{fan2010sharp} for details.}
\todo[inline]{Need a sentence saying what the results are: at least such and such percent benefit from forced commitment}

%An alternative way of presenting the \cite{fan2010sharp} bounds is in terms of quantiles of the distribution of $\Delta$. Let $0 < q < 1$, and define $Q_0, Q_1, Q$ to be the quantile functions corresponding to $F_0, F_1$ and $F_\Delta$.\footnote{In other words, $Q_0(q) \equiv \inf \{x | F(x) \geq q\}$ and so on.} Then the sharp bound for $Q_\Delta(q)$ is given by $\underline{Q}(q) \leq Q(q) \leq \overline{Q}(q)$ where
%\[
%\overline{Q}(q) \equiv \inf_{u \in [q,1]} [Q_1(u) - Q_0(u - q)], \quad
%\underline{Q}(q) \equiv \sup_{u\in [0,q]} [Q_1(u) - Q_0(1 + u - q)]
%\]
%By substituting $q = 0.11$, these expressions allow us to bound the 11th percentile of the distribution of $\Delta$. Under a stylized Roy model in which borrowers with the largest (negative) treatment effects choose commitment, $Q(0.11)$ equals the treatment effect for the borrower at the margin of indifference between choosing commitment. 
%Our point estimates for the lower and upper bounds $\underline{Q}(0.11)$ and $\overline{Q}(0.11)$ are \hl{XXXX} and \hl{XXXX} with corresponding 95\% confidence intervals \hl{XXXX} and \hl{XXXX}.\footnote{Again, confidence intervals are constructed using \hl{XXXX} bootstrap as describe in \cite{fan2010sharp}.}
%%\todo[inline]{Issac: add the interval for $Q(0.11)$. Again, this needs to be without covariates and we need to be careful about the sign convention for our effects. Maybe we don't need a second figure with the confidence bands for the whole quantile function. Frank: add a sentence or two discussing the results. Presumably the aforementioned quantile is indeed negative and fairly large.}
%Both ways of presenting the bounds yield the same conclusion: at least some borrowers who would benefit from commitment \emph{do not choose it} when offered.

@@

Our assumption-free bounds from the preceding section show that more than 11\% of borrowers would benefit from a policy of forced commitment. 
Intuitively, this seems to suggest that some of the 89\% of borrowers in the choice arm who did \emph{not} choose commitment would have faced lower borrowing costs if they had.
Making this intuition precise, however, requires a careful consideration of the relationship between choice and heterogeneous treatment effects. 
To this end, we now provide a full definition of the potential outcomes in our empirical setting, and introduce a pair of assumptions that will allow us to go beyond the assumption-free bounds from above.

Let $Z_i \in \{0, 1, 2\}$ denote the treatment arm to which to participant $i$ was assigned: $Z_i = 0$ denotes the forced no-commitment arm, $Z_i = 1$ denotes the forced commitment arm, and $Z_i = 2$ denotes the choice arm. 
Now let $D_i$ be the treatment that participant $i$ actually \emph{received}, where $D_i = 0$ denotes no-commitment and $D_i = 1$ denotes commitment. 
We assume perfect compliance in the $Z_i = 0$ and $Z_i = 1$ arms.\footnote{For more discussion on this point, see Section \ref{sec:integrity} above.}
It is only in the $Z_i = 2$ arm that participants are free to choose between alternative contracts. 
Let $C_i \in \{0, 1 \}$ denote a participant's ``choice type.'' If $C_i = 1$ then participant $i$ \emph{would choose commitment}, given the option; if $C_i = 0$ she would not. 
As shorthand, we call borrowers with $C_i = 1$ ``choosers'' and those with $C_i = 0$ ``non-choosers.''
Whereas a participant's choice type $C_i$ is only observed if she is allocated to the choice arm ($Z_i = 2$), her treatment $D_i$ and experimental arm $Z_i$ are always observed. 
Given the design of our experiment, these quantities are related by
\begin{equation}
D_i = \mathbbm{1}(Z_i \neq 2) Z_i + \mathbbm{1}(Z_i = 2) C_i.
\label{eq:potentialTreatments}
\end{equation}

We maintain the stable unit treatment value assumption (SUTVA) throughout. 
This means that borrower $i$'s outcomes depend only on her \emph{own} values of $Z_i$ and $D_i$, not those of any other person in the experiment: there are no \emph{spillovers}. 
Under this assumption, a fully general model for the potential outcomes in our experiment would take the form $Y_i(d, z)$ for $d\in \{0,1\}$ and $z \in \{0, 1, 2\}$, allowing participant $i$'s potential outcome to depend \emph{both} on the treatment she actually receives, $D_i$, and the experimental arm to which she is assigned, $Z_i$. 
This model is too general, however, to point identify meaningful causal effects. 
For this reason, we consider two exclusion restrictions.

Before stating these restrictions, we first define some additional notation.
Because our experimental design implies that any borrower with with $Z_i = 0$ has $D_i = 0$, we abbreviate the potential outcome $Y_i(d=0,z=0)$ as $Y_{i0}$. 
Similarly, since any borrower with $Z_i = 1$ has $D_i = 1$, we abbreviate $Y_i(d=1,z=1)$ as $Y_{i1}$. 
This is in keeping with our notation from section \ref{sec:bounds} above.
Using this notation, our first exclusion restriction is given by
\begin{equation}
Y_i(d=0,z=2) = Y_i(d=0,z=0) \equiv Y_{i0}.
\label{eq:exclusion0}
\end{equation}
Equation \ref{eq:exclusion0} only restricts the potential outcomes of non-choosers,  individuals with $C_i = 0$, because they are the only borrowers for whom $D_i = 0$ when $Z_i = 2$.
In words, this condition assumes that every non-chooser experiences the same potential outcome regardless of whether she is assigned to the choice arm or the control arm.
Similarly, our second exclusion restriction is given by
\begin{equation}
Y_i(d=1,z=2) = Y_i(d=1,z=1)\equiv Y_{i1}.
\label{eq:exclusion1}
\end{equation}
Equation \ref{eq:exclusion1} only restricts the potential outcomes of choosers, individuals with $C_i =1$, because they are the only borrowers for whom $D_i = 1$ when $Z_i = 2$.
In words, this condition assumes that every chooser experiences the same potential outcome regardless of whether she is assigned to the treatment arm or the choice arm.

Mathematically \eqref{eq:exclusion0} and \eqref{eq:exclusion1} have the same structure as the standard LATE exclusion restriction that $Y_i(d,z)$ depends only on $d$, not on $z$. 
Substantively, however, they are slightly different, given that there is no explicit reference to the ``chosen'' versus ``forced'' treatment distinction in the usual LATE setup.\footnote{For related discussion, see \cite{chamberlain2011bayesian} who uses an assumption similar to our exclusion restrictions to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.} 
In essence, \eqref{eq:exclusion0} and \eqref{eq:exclusion1} assume that being assigned a particular treatment has the same result as choosing it for yourself, provided that you are assigned the same treatment that you \emph{would have chosen}. 
If the mere fact of having been given a choice has a direct effect on outcomes, one or both of our exclusion restrictions will be violated.
One can imagine situations in which this might be the case.
For example, even someone who would have voluntarily chosen to undergo drug rehabilitation, given the choice, might respond differently when coerced.
In our empirical setting, however, both \eqref{eq:exclusion0} and \eqref{eq:exclusion1} are plausible. 
Moreover, each has testable implications that we fail to reject.
For details, see Appendix \ref{append:exclusion}.

Under the exclusion restrictions from \eqref{eq:exclusion0} and \eqref{eq:exclusion1}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to  
\begin{equation}
    Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right].
\label{eq:potentialOutcomes}
\end{equation}
Equation \ref{eq:potentialOutcomes} is the key to understanding the results that follows. 
As noted above, by randomly assigning $Z_i=0$ and $Z_i = 1$ our experiment identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$ in the population as a whole. 
By randomly assigning $Z_i=2$, it likewise point identifies the share of choosers ($C_i = 1$), the distribution of $Y_{i1}$ for choosers, and the distribution of $Y_{i0}$ for non-choosers ($C_i = 0$).
Because $Z_i$ is assigned independently of pre-treatment covariates $X_i$, our design also identifies the corresponding \emph{conditional} distributions of $Y_{i0}$ and $Y_{i1}$ given $X_i$. 
%These distributions are the ingredients that we use below to explore the importance of paternalism.

@@

%Above we used outcome data from the forced arms ($Z_i\neq 2$) along with the commitment take-up rate in the choice arm ($Z_i = 2$) to argue that at least some of the \hl{89\%} of participants who did \emph{not} choose commitment would have been better off if they had. 
%By additionally examining \emph{outcome data} in the choice arm, it is possible to say more. 
We now show how our experimental design, henceforth the ``controlled choice design,'' combined with the exclusion restrictions from \eqref{eq:exclusion0} and \eqref{eq:exclution1} can be used to point identify a number of interesting and economically-relevant causal quantities without the need for additional structural restrictions.
First we identify the treatment on the treated (ToT) and treatment on the untreated (TuT) effects, defined as follows:
\[
\text{ToT} \equiv \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 1), \quad
\text{TuT} \equiv \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0).
\]
%The TuT and ToT effects are particularly interesting for understanding the importance of paternalism. 
If the TuT is positive, this means that those who did not choose commitment would have experienced better outcomes, \emph{on average}, if they had. 
In a canonical Roy model, the ToT should exceed both the TuT and average treatment effect (ATE).
If the ToT is statistically distinguishable from and substantially larger than the TuT, this provides empirical support for the relevance of selection-on-gains in real-world decision-making.
Because our design identifies all three quantities, it allows us to test this implication directly and to calculate the average selection on gains (ASG):
\[
\text{ASG} \equiv \mathbbm{E}[Y_{i1} - Y_{i0}|C_i = 1] - \mathbb{E}[Y_{i1} - Y_{i0} | C_i = 0] = \text{ToT} - \text{TuT}.
\]
The controlled choice design also identifies both the average selection bias (ASB) and the average selection on levels (ASL). 
\[
\text{ASB} \equiv \mathbbm{E}[Y_{i0}|C_i = 1] - \mathbbm{E}[Y_{i0}|C_i = 0], \quad 
\text{ASL} \equiv \mathbbm{E}[Y_{i1}|C_i = 1] - \mathbbm{E}[Y_{i1}|C_i = 0].
\]
A companion STATA package accompanying this paper provides estimators of the ToT, TUT, ASG, ASB, and ASL, along with cluster-robust standard errors for each.\footnote{See Appendix \ref{append:randchoice} for more details.}

@@

%\todo[inline]{Possibly add some discussion here of Craig's idea: using the controlled choice design to study ``targeting''}

@@

Table \ref{tot_tut} calculates the causal quantities described above--ToT, TuT, ASG, ASB, and ASL--for our experimental data, along with robust standard errors for each. 
For purposes of comparison, the table also presents the ATE results from Section \ref{experiment} above (row 1), along with the corresponding average potential outcomes $\mathbbm{E}[Y_0]$ and $\mathbbm{E}[Y_1]$ (rows 4--5).
The columns of the table correspond to different outcome variables, defined as in Section \ref{costs} above.
For all four outcome definitions, the TuT effect is positive, statistically and economically significant, and comparable in magnitude to the ATE.
In other words: commitment is \emph{beneficial}, on average, to the people who \emph{would not choose it}, and these benefits are large.
The estimated ToT effects are positive and larger still.
Although we cannot quite reject the null hypothesis that the TuT and ToT effects are equal--our power is limited because of the low take-up rate of commitment in the choice arm--the pattern of coefficients is consistent with some degree of selection-on-gains.
Commitment is more beneficial to people who are willing to choose it than it is to people who are not.
For the APR benefit and (1 - Default) outcomes, we have sufficient precision to conclude that the average selection bias (ASB) is large and \emph{negative}.
This means that borrowers who choose commitment would have faced a \emph{higher} APR and probability of default under the status quo contract than borrowers who do not choose commitment. 
Overall, Table \ref{tot_tut} suggests that commitment works and the ``right people'' choose to commit: those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo. At the same time, \emph{not enough} people choose to commit: the commitment contract is beneficial on average even to those who would \emph{not} choose it voluntarily. Below we explore possible explanations for this result.

@@

\begin{figure}[H]
    \caption{Determinants of choice}
    \label{determinants_choose}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/determinants_choose_commitment.pdf}
    \end{subfigure}
    \end{center}
      \scriptsize

      The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment. Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm. 
%\textit{Do file: } \texttt{determinants_choice_sure_confidence.do}       
\end{figure}

@@

%\textit{Do file: } \texttt{fan\_park\_bnds.do}       
\end{figure}

\begin{figure}[H]
    \caption{Determinants sure confidence}
    \label{determinants_sure}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/determinants_confidence_100.pdf}
    \end{subfigure}
    \end{center}
      \scriptsize
